Tracing the Stellar Halo of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using the Hyper Suprime-Cam

### 2017-04-17 draft/paper1.tex
Method: SED fitting

% Commenting:
\newcommand{\xxx}[1]{\textcolor{red}{\textbf{XXX}}}
\newcommand{\todo}[1]{\textcolor{red}{\textbf{TODO:~#1}}}
\newcommand{\plan}[1]{\textcolor{cyan}{#1}}
\newcommand{\addref}{{\textcolor{red}{REF}}}
\newcommand{\note}[2]{\textcolor{blue}{\textbf{[Comment (#1): #2]}}}
\newcommand{\song}[1]{\textcolor{magenta}{\textbf{[Song: #1]}}}
\newcommand{\alexie}[1]{\textcolor{blue}{\textbf{[Alexie: #1]}}}
\newcommand{\jenny}[1]{\textcolor{Bittersweet}{\textbf{[Jenny: #1]}}}
\newcommand{\kevin}[1]{\textcolor{green}{\textbf{[Kevin: #1]}}}
\newcommand{\update}[1]{\textcolor{Bittersweet}{#1}}
%\newcommand{\update}[1]{#1}

@@

    Magnitudes use the AB system (\citealt{Oke1983}), and are corrected for Galactic 
    extinction using calibrations from \citet{Schlafly11}.
    In this work, we assume $H_0$ = 70~km~s$^{-1}$ Mpc$^{-1}$, ${\Omega}_{\rm m}=0.3$, 
    and ${\Omega}_{\rm \Lambda}=0.7$.
    Stellar mass is noted \mstar{} and has been derived using a Chabrier Initial Mass 
    Function (IMF; \citealt{Chabrier2003}).     
    $M_{\mathrm{halo}}$ denotes halo mass in general whereas $M_{\rm 200b}$ is 
    explicitly defined as $M_{\rm 200b}\equiv M(<r_{\rm 200b})=200\bar{\rho} 
    \frac{4}{3}\pi r_{\rm 200b}^3$ where $r_{\rm 200b}$
    is the radius at which the mean interior density is equal to 200 times
    the mean matter density ($\bar{\rho}$).

@@

    In this work, we derive average \m2l{} using the Flexible Stellar Population 
    Synthesis\footnote{http://scholar.harvard.edu/cconroy/sps-models}
    (FSPS; \texttt{v2.4}; \citealt{FSPS}, \citealt{Conroy2010}) model based on the MILES
    \footnote{http://www.iac.es/proyecto/miles/pages/stellar-libraries/miles-library.php}
    (\citealt{MILES1}, \citealt{MILES2}) stellar library and assuming a
    \citet{Chabrier2003} IMF between 0.1 to 100 \msun. 
    The star formation history (SFH) is assumed to follow a delayed-$\tau$ model with 
    stochastic star bursts (see Appendix~\ref{app:sed}). 
    This SFH is appropriate for massive galaxies at low redshifts 
    (e.g.\ \citealt{Kauffmann2003}). 
    For stellar metallicity, we assume a flat distribution between 0.004 to 0.03 
    (the highest value allowed by FSPS) \jenny{define metallicity here, means different things sometimes}. 
    We adopt the \citet{Calzetti2000} extinction law with a order two Gamma 
    distribution of $A_{V}$ between 0 to 2 magnitude. 
    A majority of our galaxies are red and quiescent and our results are 
    not very sensitive to parameters related to the SFH or the internal dust extinction. 
    To achieve reasonable sampling across these parameters, we generate 250000 models.

    We construct five band SEDs using the forced-photometry \cmodel{} magnitudes 
    corrected for Galactic extinction. 
    \cmodel{} only accounts for the statistical error on the flux measurement but does
    not account for systematic uncertainties in the model-fitting process. 
    It therefore underestimates the flux errors of bright galaxies. 
    Based on tests using synthetic objects, we find that the average accuracy of
    \cmodel{} for a bright galaxy is $\sim 1$\% in the $r$, $i$, $z$ bands, 
    and slightly worse in the $g$ and Y-band. 
    Therefore, we supply \texttt{iSEDFit} with simplified flux errors assuming 
    $S/N = 100$ for the $riz$ bands, and $S/N = 80$ for the $g$Y bands (on average, 
    images in $gY$ bands are shallower in depth and/or have higher background noise).  
    The typical uncertainty of \logms{} is around 0.08-0.10 dex at \logms${\sim} 11.5$. 
    Please see Appendix~\ref{app:sed} for further details.

@@

    Using the best-fit stellar mass from \texttt{iSEDFit} (noted as as \mcmodel{}), 
    we estimate the average \m2l{} in the $i$-band, then use that \m2l{} to convert our 
    1-D luminosity density profiles into stellar mass density profiles. 
    We also convert our 10 and 100 kpc aperture luminosities into corresponding stellar 
    mass estimates (noted as \minn{} and \mtot{}).

    For the remainder of this paper, we will use \mtot{} as a proxy of ``total'' 
    stellar mass. \jenny{Here is where we need discussion of Figure \ref{fig:mass_diff} I think? When do 
    we discuss cModel magnitudes?}
	\jenny{Check me here!}
    In Appendix~\ref{app:sedasic}, we briefly summarize the basic statistics of 
    the sample using our estimates of \mtot{} and \minn{}.
    We confirm that the sample follows a very tight ``red-sequence'' that does not appear to depend on 
    environment (see \S XX). 
    Appendix~\ref{app:sed} describes the outputs from our SED fitting process 
    (average stellar age, metallicity, and internal dust extinction). 
    We do not utilize these quantities in this paper, but we have checked that they all 
    behave reasonably for both samples. 
    As expected, the integration of the 1-D profile out to very large radius recovers 
    more luminosity (stellar mass) compared to the \cmodel{}-based estimates. 
    This will be shown in Section \ref{ssec:s82}.

>>>>

% Commenting:
\newcommand{\xxx}[1]{\textcolor{red}{\textbf{XXX}}}
\newcommand{\todo}[1]{\textcolor{red}{\textbf{TODO:~#1}}}
\newcommand{\plan}[1]{\textcolor{cyan}{#1}}
\newcommand{\addref}{{\textcolor{red}{REF}}}
\newcommand{\note}[2]{\textcolor{blue}{\textbf{[Comment (#1): #2]}}}
\newcommand{\song}[1]{\textcolor{magenta}{\textbf{[Song: #1]}}}
\newcommand{\alexie}[1]{\textcolor{blue}{\textbf{[Alexie: #1]}}}
\newcommand{\jenny}[1]{\textcolor{Bittersweet}{\textbf{[Jenny: #1]}}}
\newcommand{\kevin}[1]{\textcolor{green}{\textbf{[Kevin: #1]}}}
\newcommand{\update}[1]{\textcolor{OliveGreen}{#1}}
%\newcommand{\update}[1]{#1}

@@

    Magnitudes use the AB system (\citealt{Oke1983}), and are corrected for Galactic 
    extinction using calibrations from \citet{Schlafly11}.
    In this work, we assume $H_0$ = 70~km~s$^{-1}$ Mpc$^{-1}$, ${\Omega}_{\rm m}=0.3$, 
    and ${\Omega}_{\rm \Lambda}=0.7$.
    Stellar mass is noted \mstar{} and has been derived using a Chabrier Initial Mass 
    Function (IMF; \citealt{Chabrier2003}).

    %$M_{\mathrm{halo}}$ denotes halo mass in general whereas $M_{\rm 200b}$ is 
    %explicitly defined as $M_{\rm 200b}\equiv M(<r_{\rm 200b})=200\bar{\rho} 
    %\frac{4}{3}\pi r_{\rm 200b}^3$ where $r_{\rm 200b}$
    %is the radius at which the mean interior density is equal to 200 times
    %the mean matter density ($\bar{\rho}$).

@@

    In this work, we derive average \m2l{} using the Flexible Stellar Population 
    Synthesis\footnote{http://scholar.harvard.edu/cconroy/sps-models}
    (FSPS; \texttt{v2.4}; \citealt{FSPS}, \citealt{Conroy2010}) model based on the 
    MILES\footnote{http://www.iac.es/proyecto/miles/pages/stellar-libraries}
    (\citealt{MILES1}, \citealt{MILES2}) stellar library and assuming a
    \citet{Chabrier2003} IMF between 0.1 to 100 \msun. 
    The star formation history (SFH) is assumed to follow a delayed-$\tau$ model with 
    stochastic star bursts (see Appendix~\ref{app:sed}). 
    This SFH is appropriate for massive galaxies at low redshifts 
    (e.g.\ \citealt{Kauffmann2003}). 
    \update{
    For stellar metallicity 
    ($[\mathrm{M}/\mathrm{H}]=\log\ \mathrm{Z}/\mathrm{Z}_{\odot}$), we assume a flat 
    distribution between 0.004 to 0.03 (the highest value allowed by FSPS).
    } 
    We adopt the \citet{Calzetti2000} extinction law with a order two Gamma 
    distribution of $A_{V}$ between 0 to 2 magnitude. 
    A majority of our galaxies are red and quiescent and our results are 
    not very sensitive to parameters related to the SFH or the internal dust extinction. 
    To achieve reasonable sampling across these parameters, we generate 250000 models.

    We construct five band SEDs using the forced-photometry \cmodel{} magnitudes 
    corrected for Galactic extinction. 
    \cmodel{} only accounts for the statistical error on the flux measurement but does
    not account for systematic uncertainties in the model-fitting process. 
    It therefore underestimates the flux errors of bright galaxies. 
    For this work, we supply \texttt{iSEDFit} with simplified flux errors assuming 
    $S/N = 100$ for the $riz$ bands, and $S/N = 80$ for the $g$- and $y$-band 
    (on average, images in $gy$ bands are shallower in depth and/or have higher 
    background noise).  
    Although thse are still conservative estimates of the systematic uncertainties 
    involved in the model-fitting, tests using synthetic galaxies show that \cmodel{}
    provides excellent measurements of five-band colors, which are crucial for reliable
    \m2l{} estimates.
    The typical uncertainty of \logms{} is around 0.06-0.08 dex at \logms${\sim} 11.5$. 
    Please see Appendix~\ref{app:sed} for further details.

@@

    Using the best-fit stellar mass from \texttt{iSEDFit} (noted as as \mcmodel{}), 
    we estimate the average \m2l{} in the $i$-band, then use that \m2l{} to convert 
    our 1-D luminosity density profiles into stellar mass density (\mden{}) profiles. 
    We also convert our 10 and 100 kpc aperture luminosities into corresponding stellar 
    mass estimates (noted as \minn{} and \mtot{}).

    For the remainder of this paper, we will use \mtot{} as a proxy of ``total'' 
    stellar mass.

    In Appendix~\ref{app:sedasic}, we briefly summarize the basic statistics of 
    the sample using our estimates of \mtot{} and \minn{}.
    We confirm that the sample follows a very tight ``red-sequence'' that does not appear to depend on 
    environment (see \S XX). 
    Appendix~\ref{app:sed} describes the outputs from our SED fitting process 
    (average stellar age, metallicity, and internal dust extinction). 
    We do not utilize these quantities in this paper, but we have checked that they all 
    behave reasonably for both samples. 
    As expected, the integration of the 1-D profile out to very large radius recovers 
    more luminosity (stellar mass) compared to the \cmodel{}-based estimates. 
    This will be shown in Section \ref{ssec:s82}.
